Thoughts about cognition

### 2015-11-05 cogniveProcessing/summery.tex
added some more, givig up

\paragraph{Do we use it?} Contraceptives seem to interfere with natural mate
selection: A big deal because similiar MHC tends to reduce succesfull
pregnacies.

\subsubsection{Receptive fields}
Description depends on modality. Somatosensory, Auditory, Visual, Gustation.

@@

>>>>

\paragraph{Do we use it?} Contraceptives seem to interfere with natural mate
selection: A big deal because similiar MHC tends to reduce succesfull
pregnacies.
\subsubsection{Transduction}
converts physical (in real world, such as sound or pressure) signals to neural
It can use chemical mechanical both or neither.

\subsubsection{Transfer}
From the transduction, to the brain, or CPU.
%I guess a brain counts as a
%processing unit and its pretty central so, yeah CPU fits fine.

\subsection{Receptive fields}
Description depends on modality. Somatosensory, Auditory, Visual, Gustation.

@@

\subsubsection{space}
The relation to space is well maintained in early sensory processing.

\subsubsection{response profiles}
What is the relation between a stimulus and a response?  Its an S curve.
How is the strenth of an external stimulus related to its proccessing?

\subsection{Adoptation}
Sensory responses are not stable over time.

The frequency of output of a snesory cell goes down over time. After
excitiation
the cell becomes more negative, becuase it pushed out all these postive ions
that entered during the spike. In the period just after the spike no positive
ions are allowed in. This makes it harder to reach the threshold for an
action potential.

Neurons adapted to their prefered stimulus are hyperpolarized. Repatitive
presynaptic stimulation depletes a readily releasable vescile pool.
It takes time to refill the readily releasable pool.

\subsection{Simple \& complex signals}
Neurons are used for information processing. They take information from
one or multiple sources and trn it into something else. Usually a more
complex form of information.

\paragraph{But} perception does not coincide with reality. Think of all the
illusions you may have seen on the web.

\subsubsection{Light reaches the retina}
Beofre light reaches the lens it already gets transformed. The cornea
(outside harder part) filters UV-light. Another interseting feature is the
layout. The axons of ganglion cells, which sends onfio to the brain,
are actually in front of the recoptors that decode light.
This already has a profound effect on vision the blindspot.

\subsubsection{Responding to light}
1 type of photo recoptors: rods and cones. They differ in the type of light
they respond to. They prefer different wave lengths. The cones will later
be used to figure out color. The rods are more sensitive to light, and
are used mostly in dark envioronments. They respond to light rather simliarly.
Both are filled with pgiments and this pigment is what gets effected by light.
Photons kind of destroy it.
